---
title: "all_functions"
output: html_document
---

cat(): 
paste()
  sep=
  collapse="" # concatenate elements of a vector into a single string
paste0(): no separator
sprintf()

nchar()
substr()
strsplit()
grep()
gsub()

set.seed(42)
runif(n, min, max): generates random num from a uniform distribution
rnorm(n, mean, sd): generates random numbers from a normal distribution
rbinom(n, sze, prob): binomial distribution
rexp(n, lambda): exponential distribution
rpois(): Poisson distribution
sample(start:end, n, replace=)

my_function <- function(arguments) {
  function statements
  return()
}

```{r}
```
ATOMIC VECTOR
is.atomic(x): returns TRUE if x is an atomic object
  list and expression are NOT atomic, just vectors
is.vector(x): returns TRUE if x is a vector
sapply(vector, typeof)
length() = number of elements

splice
vec[start:end] = splicing
vec[c(1:2, 4)] = splice the 1, 2, and 4th
vec[c(TRUE, FALSE, FALSE)] = splice the 1st
vec[vec > num] = return the elements greater than that num

modify/add
vec[2] <- 100 # modify an element
append(vec, element, after=) #add an element at a specific location
new_vec <- c(vec, value1, value2) # expand a vector

remove
vec <- vec[-position]
vec <- vec[-c(1:3, 5)]

sapply(vec, function)
  sapply(vec, function(x) x**2) # outputs the square of each element
length(vec) = number of elements
unique(vec) = remove duplicate values
sort(vec) = sorts in ascending order
rev(vec) = reverses the order of elements

rep(num/vec, #repeat) 
  rep(x, times) # repeat 4 ten times
which(vec == 8) #find indices of TRUE elements in a vector
  which.max(vec)
  which.min(vec)

results_add <- vec1 + vec2
  if one vec is shorter, R recycles it

```{r}
```
MATRIX
matrix(start_num:end_num, nrow=, ncol=, byrow=TRUE/FALSE)

dim(mat) = c(rows, cols)
length(mat) = number of elements
nrow(mat)
ncol(mat)

rownames(mat) <- c("row1", "row2",...)
colnames(mat)

cbind(mat, new_col=c(1,2,3)): add by column
  the new column will have colname "new_col"
rbind(): add by row

mat_new <- mat_new[-row, -col]
apply()
  row_sum <- apply(my_matrix, 1, sum) # sum the rows
  col_sum <- apply(my_matrix, 2, sum) # sum the cols

"val" %in% mat # check if value is in mat

```{r}
```
LIST
list() # create a list

[] and [[]]
  [] returns a sublist (many elements)
  [[]] returns the element itself (only one element)

names(lst) <- c("name1", "name2",...)
lst$name1

unlist() = convert a list to an atomic vector
lapply() and sapply() = apply a function over elements
  lapply(): returns a list
  sapply(): returns a vector or a matrix


```{r}
```
DATA FRAMES
each column can have a diff type
data.frame() # creation

df$col_name # access a col
def[row_name, ] # access a row

filter_df <- subset(df, col_name > value)































